---
title: "ECP8500"
author: "Kyle Baron"
output: 
  templ::mrg_beamer: 
    toc: false
---


```{r,setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE)
```

# ECP8500 / NHANES

## Sources of variability 

- data simulated from a _model_

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 4}
library(mrgsolve)
library(dplyr)
library(ggplot2)
library(patchwork)
theme_set(theme_bw())

mod <- modlib("popex") %>% param(TVV = 20, TVCL = 0.5, TVKA = 0.7)
mod <- omat(mod, dmat(0.03, 0.4, 0.4))
data <- expand.ev(amt = 1000, WT = rlnorm(3000, log(80), sqrt(0.1)), ii = 24, ss = 1)
out <- mrgsim(mod, data, output = "df", end = 72, delta = 0.1, add = 0.25)
out <- filter(out, DV > 0.05)
sims <- group_by(out,time) 
sims <- summarise(sims, med = median(DV), lo = quantile(DV, 0.025), 
                 hi = quantile(DV, 0.975))
#sims <- slice(sims, -c(1))
p1 <- ggplot(sims, aes(x = time)) + 
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.5, 
              fill = "cornflowerblue") + 
  geom_line(aes(y = med), lwd = 1.5) + ylim(0, NA) + 
  scale_x_continuous(breaks = seq(0,96,6)) + 
  ylab("Concentration (ng/mL)") + xlab("Time (hour)") 
p1
```


## Narrow in on 24 hours post dose

```{r, echo = FALSE, fig.height = 4}
sims <- filter(out, time %in% c(0, 3, 8, 12, 24, 36, 48, 72))
summ <- group_by(sims, time) %>% summarise(med = median(DV))
p2 <- ggplot(data = sims, aes(x = time, y = DV)) + 
  geom_point(position = position_jitter(0.5)) + 
  #scale_y_log10() + 
  geom_point(data = summ, aes(time, y = med), size = 4, color = "firebrick") + 
  geom_line(data = summ, aes(time, y = med), lwd = 1.5, color = "firebrick") + 
  scale_x_continuous(breaks = c(0, 3, 8, 12, 24, 36, 48, 72)) + 
  ylab("Concentration (ng/mL)") + xlab("Time (hour)")
p2
```


---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
sims24 <- filter(sims, time==24)
ggplot(data = sims24, aes(x = DV)) + 
  geom_histogram(color = "white", alpha = 0.9) + 
  xlab("Ctrough (ng/mL)") + 
  scale_x_continuous(breaks = seq(0,150,10))
```


## NHANES

- National 
- Health 
- And 
- Nutrition 
- Examination
- Survey


> "a program of studies designed to assess the health and nutritional status of adults and children in the United States"

https://www.cdc.gov/nchs/nhanes/index.htm

---

- Survey 5000 people each year
- Counties across the US
  - 15 each year

- Interview
  - conducted in respondents' homes
  - demographic, socioeconomic, dietary, and health-related questions
- Examination
  - performed in mobile centers which travel to locations around the country
  - medical, dental, and physiological measurements,  laboratory tests
